Airbnb Predictions Project

### 2019-01-03 content/post/2019-01-02-transit.Rmd

---
title: Transit
author: Effi Feldblum
date: '2019-01-02'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

>>>>

---
title: A Question on the Efficiency of Transit in Absurd Situations
author: Effi Feldblum
slug: transit
description: A short Article
summary: AAAA
date: '2018-08-22'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

### 2019-01-03 content/post/article.Rmd

---
title: "Airbnb Predictions Project"
author: "Effi Feldblum"
date: '2018-12-10'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

>>>>

---
title: Airbnb Predictions Project
author: Effi Feldblum
slug: airbnb
description: A short Article
summary: AAAA
date: '2018-12-10'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
